---
title: "bootstrapping"
author: "Tara Ahi"
date: "12/4/2021"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.clour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

sclae_colour_discrete = scale_color_viridis_d()
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

**Boostrapping in SLR**

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

Make a plot

```{r}
sim_df_const %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

linear model of y against x

```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```
_intercept is 2, slope is about 3, SE for slope is about 0.7_

Getting good slope but bad SEs, let's try to use the bootstrap:

sample_frac tells it the proportion/size you want (we want the same one we started with, 1. we want replace = true)

```{r}
sim_df_nonconst %>% 
  sample_frac(size = 1, replace = TRUE) %>% 
  arrange(x)
```
This is what we get when we draw from sample with replacement, it'll change slightly each time you run it.







