---
title: "linear_models"
author: "Tara Ahi"
date: "11/19/2021"
output: html_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


Load NYC Airbnb data, clean/mutate/filter

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```


Visualizations...

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```


Fit a linear model...

price against stars and borough
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Take a look at it...

```{r}
fit
```

Zero star refrence group has price of $70, each star rating adds about 30 dollars

```{r}
summary(fit)
summary(fit)$coef

fit %>% broom::tidy()
```

Get some additional info with summary

If you want to present output... (add kable for nice view)

```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```


## Diagnostics

```{r}
modelr::add_residuals(nyc_airbnb, fit)
```

Added residuals column, which returns observed data point from fitted value. 


```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = resid)) +
  geom_density() +
  xlim(-200, 200)
```

or

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) + geom_violin()
```

or

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()
```


Skipping over hypothesis testing... could use something like this

```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```


## Interactions

Let's try to fit a different model ...

```{r}
fit = lm(price ~ stars + room_type, data = nyc_airbnb)

broom::tidy(fit)
```

Now with interaction

```{r}
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

broom::tidy(fit)
```

lots of coefficients, we could use nested datasets and then map across those datasets to build regression models that we care about:


## Nesting

```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x))
  )
```
We've created a little dataset that I'm interested in, easier to work with.
The mutate means you're mapping across the data column some function. We have to say price is a function of stars and room type. The `.x` is wherever we want the object to go, object being the linear model I think. 


The lm results are a bit of a mess so we add another line to tidy:

```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(borough, lm_results) %>% 
  unnest(lm_results) %>% 
  filter(term == "stars")
```
Now we have a 4x5 dataframe.
Then we can just selet borough and lm results since we dont' care about the data, unnest the results, gives dataframe of what effect of stars is in each region.
Can then specify the effect of stars.


Let's look at neighborhoods in Manhattan...

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  select(-borough) %>% 
  relocate(neighborhood) %>% 
  nest(data = price:room_type)
```
So for every neighborhood in Manhattan, we see all the variables for the listings (90 air bnbs in flatiron, etc). Dataframe has a column of dataframes.



Effect of room type on outcome, adjusting for stars
```{r}
manhattan_lm_results_df = 
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  select(-borough) %>% 
  relocate(neighborhood) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(neighborhood, lm_results) %>% 
  unnest(lm_results)
```


neighborhood-specific estimates for the coefficients related to room type:

```{r}
manhattan_lm_results_df %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_grid(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


Getting estimates of impact of increasing star rating on price, adjusting for room type, making denisty plot:

```{r}
manhattan_lm_results_df %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) +
  geom_density()
```
Seems like across all neighborhoods, increasing stars doesn't have a big effect-- some places it goes up a lot, sometimes it becomes cheaper. 








